% vim: nowrap fdm=marker foldlevel=0 tw=0
% {{{
{\color{gray}
\bibitem[BiCS(2018a)]{bics-bsp-report-template}
\newblock {BiCS Bachelor Semester Project Report Template.}
\newblock \url{https://github.com/nicolasguelfi/lu.uni.course.bics.global}
\newblock {University of Luxembourg, BiCS - Bachelor in Computer Science (2017).}

\bibitem[BiCS(2018b)] {bics-bsp-reference-document}
\newblock {Bachelor in Computer Science}:
\newblock {BiCS Semester Projects Reference Document}.
\newblock Technical report, University of Luxembourg (2018)

\bibitem[Armstrong and Green(2017)]{armstrong2017guidelinesforscience}
\newblock J~Scott Armstrong and Kesten~C Green.
\newblock Guidelines for science: Evidence and checklists.
\newblock \emph{Scholarly Commons}, pages 1--24, 2017.
\newblock \url{https://repository.upenn.edu/marketing\_papers/181/}
}
% }}}


\bibitem {modalities}
\newblock {Impact of Multiple Modalities on Emotion Recognition: Investigation into 3D Facial Landmarks, Action Units, and Physiological Data.}
\newblock {\it Diego Fabiano, Manikandan Jaishanker and Shaun Canavan}

\bibitem {synthesis-model}
\newblock {Deformable Synthesis Model for Emotion Recognition.}
\newblock {\it Diego Fabiano and Shaun Canavan}

\bibitem {spatiotemporal-features}
\newblock {Emotion Recognition using Spatiotemporal Features from Facial Expression Landmarks.}
\newblock {\it Hamid Golzadeh, Diego R. Faria, Luis J. Manso, Anikó Ekárt and Christopher D. Buckingham}

\bibitem {electronics}
\newblock {Facial Landmark-Based Emotion Recognition via Directed Graph Neural Network.}
\newblock {\it Quang Tran Ngoc, Seunghyun Lee and Byung Cheol Song}

\bibitem {landmarks-forest}
\newblock {Facial Expression Recognition Using Facial Landmarks and Random Forest Classifier.}
\newblock {\it M. I. N. P. Munasinghe}

\bibitem {landmarks-feel}
\newblock {I Know How You Feel: Emotion Recognition with Facial Landmarks.}
\newblock {\it Ivona Tautkute, Tomasz Trzcinski and Adam Bielski}

\bibitem {stgcn}
\newblock {Spatial Temporal Graph Convolutional Networks for Skeleton-Based Action Recognition}
\newblock {\it Sijie Yan, Yuanjun Xiong and Dahua Lin}

\bibitem {survey}
\newblock {Survey on RGB, 3D, Thermal, and Multimodal Approaches for Facial Expression Recognition: History, Trends, and Affect-related Applications}
\newblock {\it Ciprian A. Corneanu, Marc Oliu, Jeffrey F. Cohn, and Sergio Escalera}

\bibitem {anatomy}
\newblock {Classic Human Anatomy in Motion: The Artist's Guide to the Dynamics of Figure Drawing; Chapter 4. Facial Muscles and Expressions}
\newblock {\url{https://doctorlib.info/anatomy/classic-human-anatomy-motion/5.html}}
