\subsection{Domains}

% \KB{Not too sure what to write here?}

Our \gls{bsp} falls into the intersection of the following domains:
Software Engineering and DevOps. In the scientific part we will briefly
explore the concepts and their relations that were of interest in this
project. In the technical domains we shall briefly present the tools
that we used for achieving our implementation and how they were relevant.

\subsubsection{Scientific}
% {\color{gray}
% Provide a description of the scientific domain(s) in which the project is being made.
% }

% \KB{The scientific domain concerns software engineering and the DevOps
% philosophy. We will briefly present the DevOps' focus on automation.
% This will be of interest for the technical domain.}

% In order to build software, there are steps preceding the actual
% technical production that have a huge impact on the overall
% product---be it from the user, developer or operator point of view.
Creating software consists among other things in finding both the
functional and non-functional requirements---the focus here lies on the
design of the product however, not its specification.
% At a later point we also
% need to start \textit{designing}. This phase is where we make
% decisions---about the product---that should ultimately lead to
% fulfilling the requirements. 
One should also think about methods and
techniques that will aid in this endeavour and think long term about
the software life cycle.

Therefore, one way to structure our software is by using the \gls{ms}
architecture which separates everything into services---as will be
discussed in section \ref{sd:ms}. Another possibility would be a
\textit{monolithic} architecture which would for example lead to
structuring according to a server-client model. For this \gls{bsp} we
decided to investigate \glspl{ms} that exist along side monoliths.

Finally, in order to facilitate the managing of \glspl{ms}, we resort
to DevOps.\cite{devops-culture} If we have multiple
services to manage, DevOps will allow us to make the process of
building, deploying, and maintaining the product fast and efficient.
Particularly interesting for us is the focus on automation and the
therefrom arising benefits as will be discussed in section
\ref{sd:devops}.

\subsubsection{Technical}
% {\color{gray}
% Provide a description of the technical domain(s) in which the project is being made.
% }

We used \textit{GitLab} as a \gls{cicd} service to support the
automation of some development activities. The \gls{e4l}
code is in fact also hosted using a GitLab platform, however it lives
on a different GitLab instance than our \gls{ms}. Deploying the
\gls{ms} would be done onto our Juno testing environment, which also
happens to be where \gls{e4l} is deployed. This does not affect the
validity of our technical productions however, since we could simply
deploy our \gls{ms} elsewhere---after all, we built and tested our
application outside of Juno.

To package our \gls{ms} we relied on \textit{docker} which allows us to create
isolated containers. Docker is in fact also what allowed us to
properly implement the \gls{ms} in itself architecture-wise.

Further, GitLab provides so-called \textit{runners} that give us the
ability to execute tasks or commands automatically. Thus we can make
it such that our \gls{ms} will be automatically redeployed any time we
make a modification. The runner can either be set up locally on the
server, or to run inside a container on the server; we ended up using
the former.

The actual application running in the \gls{ms} was written using
\textit{Python}. We used the \verb|dash| module to easily create a web page
containing a graph. Further python modules were used to make HTTPS
requests and connect to an SQL database in order to grab some data to
be plotted.  Within the \gls{ms}, we also relied on the Linux
\verb|crontab| utility to periodically grab new data during the
service's life cycle. 

Our technical contribution shows how one can deploy a \gls{ms} along
side an existing monolithic application. Further technical insights
shall be provided in section \ref{td:ms}.

% \KB{The technical domain also concerns software engineering but
%   focuses on software architectures, namely the \gls{ms} architecture.
%   Here we will briefly introduce what software architectures are and
%   how they impact the final product. For this we shall shortly
% introduce the monolithic and \gls{ms} style. The latter is the one we
% relied on for our technical productions.}
